---
title: "Area based correction of UAV data"
output: html_notebook
---

Load all the necessary packages and functions. 

```{r header, results = "hide" }
rm(list = ls())
library(mgcv)
library(UAVforestR)
library(gridExtra)
library(sp)
library(rgeos)
library(rgdal)
library(RColorBrewer)
library(spatialEco)
library(caret)

source("../../R/AGBfunctions.R")
source("../../R/min_extent.R")

htod<-function(x, tau) htod_lookup(x, lut=lut_uav, tau)

rmse<-function(x, y)  sqrt(mean((y-x)^2, na.rm=TRUE))

bias<-function(x, y)  mean(y-x, na.rm=TRUE)

# Calculates the mean while applying a coverage threshold:
mean_cover<-function(x, cover = 0.75, ...){
  cover_prop<-sum(!is.na(x))/length(x)
  if(cover_prop > cover)
    mean(x, na.rm = TRUE)
  else
    return(NA)
}

# Calcuates topographic position index:
tpiw <- function(x, w, coverage) {
  m <- matrix(1, nc=w, nr=w)
  centre_pos<-ceiling(0.5 * length(m))
  acceptable_coverage<-(w^2)*(1-coverage)
  f <- focal(x, m,  fun = function(x, na.rm){
    if(sum(is.na(x)<acceptable_coverage)){
      X<-x[centre_pos]
      x[centre_pos]<-NA
      return(X-mean(x, na.rm = TRUE))
    }
    else
      return(NA)
  },
  na.rm = TRUE,
  pad=TRUE, 
  padValue=NA)
}
```

Load the UAV and LiDAR image and ensure the UAV and LiDAR DEMs are vertically aligned (numbers from manual alignment). Any very low values in the UAV DSM are removed. Then calculate the canopy height model for the UAV


```{r load rasters and align}
uav_dsm<-raster("../../data/raster/uav_dsm_matched_cropped.tif")
uav_dtm<-raster("../../data/raster/uav_dtm_matched_cropped.tif")
lid_dsm<-raster("../../data/raster/lid_dsm_matched_cropped.tif")
lid_dtm<-raster("../../data/raster/lid_dtm_matched_cropped.tif")
lid_chm<-raster("../../data/raster/lid_chm_matched_cropped.tif")

lid_chm<-readAll(lid_chm)
lid_dtm<-readAll(lid_dtm)

# Align vertically with LiDAR:
uav_dsm<-uav_dsm-17.6
uav_dtm<-uav_dtm-17.6
# remove very low values from UAV DSM
uav_dsm[uav_dsm<0]<-NA
uav_dtm[uav_dtm<0]<-NA
# Calculates the canopy height models for the UAV
uav_chm<-uav_dsm-uav_dtm # UAV DTM

writeRaster(uav_chm, "../../data/raster/uav_chm_matched_cropped.tif", overwrite = TRUE)

# The area of the kapas tenggah survey in ha:
(sum(is.na(values(uav_chm))) * res(uav_chm)[1] * res(uav_chm)[2]) / 10000

```


```{r}
# You need to run this in the console:
plot(lid_chm)
# aoi<-drawPoly(sp=TRUE, col='red', lwd=2) # !!! You have to do this by hand on the plotted image
# proj4string(aoi)<-crs(lid_chm)
# lid_chm_croppedarea<-raster::extract(lid_chm, aoi)
#lid_chm_croppedarea<-raster::select(lid_chm)
#mean(values(lid_chm_croppedarea), na.rm = TRUE)
#sd(values(lid_chm_croppedarea), na.rm = TRUE)
```


```{r}
par(mfrow=c(1,1), mar = c(0.5,0.5,1,1))
col.pal<-list(color = colorRampPalette(brewer.pal(9,"GnBu"))(10))$color
col.breaks<-seq(0, 50, length=length(col.pal)+1)

hist(values(lid_chm))

plot(lid_chm, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)


plot(lid_dtm - uav_dtm)

```


```{r}

scale <-50 
n_pix<-as.integer(scale / res(lid_chm)[1])
w<-matrix(1, n_pix, n_pix)

uav_dsm_1ha<- aggregate(uav_dsm, fact = n_pix, fun = mean_cover)
uav_dtm_1ha<- aggregate(uav_dtm, fact = n_pix, fun = mean_cover)
lid_dtm_1ha<- aggregate(lid_dtm, fact = n_pix, fun = mean_cover)
uav_tpi_9ha<-tpiw(uav_dsm_1ha, w = 5, coverage = 0.75)

uav_dtmtpi_2.25ha<- tpiw(uav_dtm_1ha, w = 3, coverage = 0.75)
uav_dsmtpi_2.25ha<- tpiw(uav_dsm_1ha, w = 3, coverage = 0.75)
uav_dtmtpi_6.25ha<- tpiw(uav_dtm_1ha, w = 5, coverage = 0.75)
uav_dsmtpi_6.25ha<- tpiw(uav_dsm_1ha, w = 5, coverage = 0.75)

uav_tpi_25ha<-tpiw(uav_dsm_1ha, w = 5, coverage = 0.75)

par(mfrow=c(1,2))
#plot(uav_dsm_1ha)
plot(uav_tpi_9ha)
plot(uav_dtmtpi_6.25ha)
#plot(uav_tpi_25ha)

```


Extract top canopy for the LiDAR and UAV and then fit a polynomial to this. 

```{r}
lid_tch <- aggregate(lid_chm, fact = n_pix, fun = mean_cover)
uav_tch <- aggregate(uav_chm, fact = n_pix, fun = mean_cover)
uav_tch_sd <- aggregate(uav_chm, fact = n_pix, fun = sd)

```

```{r}

tch<-data.frame(lid = values(lid_tch),
                uav = values(uav_tch),
                tpi_dtm_2.25ha = values(uav_dtmtpi_2.25ha),
                tpi_dsm_2.25ha = values(uav_dsmtpi_6.25ha),
                tpi_dtm_6.25ha = values(uav_dtmtpi_6.25ha),
                tpi_dsm_6.25ha = values(uav_dsmtpi_6.25ha),
                tch_sd = values(uav_tch_sd),
                tch_cov = values(uav_tch_sd/uav_tch)
                ) %>%
  mutate(tpi = tpi_dsm_2.25ha) %>%
  mutate(lid2 = lid^2) %>%
  na.omit

cor(tch$lid,tch$uav)
bias(tch$lid,tch$uav)
rmse(tch$lid,tch$uav); rmse(tch$lid,tch$uav)/ mean (tch$lid)

# Trying to fit different functions to the untransformed LiDAR data 
tch %>% 
  mutate(myweights = abs(uav)/sum(uav)) %>%
  ggplot(aes(x = uav, y = lid, size = tpi), weight = myweights) +
  geom_point(alpha = 0.4) +
#  geom_smooth(method = "lm", formula = y~x-1) + 
  geom_smooth(method = "lm", formula = y~x) + 
  geom_smooth(method = "lm", formula = y~poly(x, 2, raw = TRUE)) + 
  # geom_smooth(method = "nls", formula = y~(a * x) / (b + x), 
              # method.args = list(start=c(a=80,b=80)),
              # se = FALSE) + 
  geom_abline(intercept = 0,slope = 1)

# After squaring the LiDAR data we can fit linear functions:
# Trying to fit different functions to the untransformed LiDAR data 
tch %>% 
  mutate(myweights = (uav^2)/sum(uav^2)) %>%
  ggplot(aes(x = uav, y = lid2, size = tpi, weight = myweights)) +
  geom_point(alpha = 0.4) +
  geom_smooth(method = "lm", formula = y~x) + 
  geom_smooth(method = "lm", formula = y~poly(x, 2, raw = TRUE)) + 
  # geom_smooth(method = "nls", formula = y~(a * x) / (b + x), 
  #             method.args = list(start=c(a=80,b=80)),
  #             se = FALSE) + 
  geom_abline(intercept = 0, slope = 40)



# Fit the polynomial linear model with cross-validation:
tch_intrain<-createDataPartition(y = tch$uav, times = 1, p = 1, list = FALSE)
tch_training<-tch[tch_intrain[,1],]
tch_testing<-tch[-tch_intrain[,1],]

nrow(tch_training)
nrow(tch_testing)


# The basic linear model
tch_fm1_cv<- train(
  lid ~ uav, tch_training,
  method = "lm",
  # weights = abs(tch_training$uav)/sum(tch_training$uav),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm1<- lm(lid ~ uav, tch_training)


# The basic linear model to LiDAR squared
tch_fm2_cv<- train(
  lid2 ~ uav, tch_training,
  method = "lm",
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm2<- lm(lid2 ~ uav, tch_training)

# The basic quadratic model:
tch_fm3_cv<- train(
  lid ~ poly(uav, 2, raw = TRUE), tch_training,
  method = "lm",
  # weights = (tch_training$uav^2)/sum(tch_training$uav^2),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm3 <-
  lm(
  lid ~ poly(uav, 2, raw = TRUE),
  # weights = (tch_training$uav ^ 2) / sum(tch_training$uav ^ 2),
  tch_training
  )

# The basic quadratic model to lidar squared:
tch_fm4_cv<- train(
  lid2 ~ poly(uav, 2, raw = TRUE), tch_training,
  method = "lm",
  # weights = (tch_training$uav^2)/sum(tch_training$uav^2),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm4 <-
  lm(
  lid2 ~ poly(uav, 2, raw = TRUE),
  # weights = (tch_training$uav ^ 2) / sum(tch_training$uav ^ 2),
  tch_training
  )

# A more complex model including tpi
tch_fm5_cv <- train(
  lid2 ~ uav * tpi, tch_training,
  method = "lm",
  # weights = abs(tch_training$uav^2)/sum(tch_training$uav^2),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm5 <-
  lm(
  lid2 ~ uav*tpi,
  tch_training
  )

tch_fm6_cv <- train(
  lid2 ~ uav * tch_sd, tch_training,
  method = "lm",
  # weights = abs(tch_training$uav^2)/sum(tch_training$uav^2),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm6 <-
  lm(
  lid2 ~ uav *tch_sd,
  tch_training
  )

# A more complex model including tpi
tch_fm7_cv <- train(
  lid ~ poly(uav,2, raw = TRUE) * tpi, tch_training,
  method = "lm",
  # weights = abs(tch_training$uav^2)/sum(tch_training$uav^2),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm7 <-
  lm(
  lid ~ poly(uav,2,raw = TRUE) *tpi,
  tch_training
  )

tch_fm8_cv <- train(
  lid ~ poly(uav, 2, raw = TRUE) * tch_sd, tch_training,
  method = "lm",
  # weights = abs(tch_training$uav^2)/sum(tch_training$uav^2),
  trControl = trainControl(
    method = "cv", number = 5,
    verboseIter = TRUE)
)
tch_fm8 <-
  lm(
  lid ~ poly(uav, 2, raw = TRUE) *tch_sd,
  tch_training
  )

# tch_fm9_cv <- train(
#   lid ~ poly(uav, 2, raw = TRUE) * tpi + poly(uav, 2, raw = TRUE) * tch_sd, tch_training,
#   method = "lm",
#   # weights = abs(tch_training$uav^2)/sum(tch_training$uav^2),
#   trControl = trainControl(
#     method = "cv", number = 5,
#     verboseIter = TRUE)
# )

# Check the cross-validated model performance:
tch_fm1_cv
tch_fm2_cv
tch_fm3_cv # 3 is better than 1... applying a polynomial is better without transformation
tch_fm4_cv # 2 is better than 4... no need to apply a polynomial after transformation

tch_fm5_cv
tch_fm6_cv
tch_fm7_cv
tch_fm8_cv

summary(tch_fm1)
summary(tch_fm2)
summary(tch_fm3)
summary(tch_fm4)
summary(tch_fm5)
summary(tch_fm6)
summary(tch_fm7)
summary(tch_fm8)


```

```{r}

# Convert any values <0 to 0
uav_tch_nozero<-uav_tch
uav_tch_nozero[uav_tch_nozero<0]<-0

uav_newdata<-stack(uav_tch_nozero, uav_dsmtpi_2.25ha, uav_tch_sd)
names(uav_newdata)<-c("uav", "tpi", "tch_sd")

# Create a raster of the predicted TCH values from model 0:
uav_tch_cor1 <- raster::predict(uav_newdata, tch_fm1)
uav_tch_cor2 <- sqrt(raster::predict(uav_newdata, tch_fm2))
uav_tch_cor3 <- raster::predict(uav_newdata, tch_fm3)
uav_tch_cor4 <- sqrt(raster::predict(uav_newdata, tch_fm4))
uav_tch_cor5 <- sqrt(raster::predict(uav_newdata, tch_fm5))
uav_tch_cor6 <- sqrt(raster::predict(uav_newdata, tch_fm6))
uav_tch_cor7 <- raster::predict(uav_newdata, tch_fm7)
uav_tch_cor8 <- raster::predict(uav_newdata, tch_fm8)

# Add these to the TCH dataframe
tch$uav_cor1<- values(uav_tch_cor1) %>% na.omit
tch$uav_cor2<- values(uav_tch_cor2) %>% na.omit
tch$uav_cor3<- values(uav_tch_cor3) %>% na.omit
tch$uav_cor4<- values(uav_tch_cor4) %>% na.omit
tch$uav_cor5<- values(uav_tch_cor5) %>% na.omit
tch$uav_cor6<- values(uav_tch_cor6) %>% na.omit
tch$uav_cor7<- values(uav_tch_cor7) %>% na.omit
tch$uav_cor8<- values(uav_tch_cor8) %>% na.omit

tch$training<-0
tch$training[tch_intrain]<-1

tch %>% 
  tidyr::gather(key = "correction", value = "uav_tch", uav, matches("uav_cor")) %>%
  # Plot the correction against the LiDAR
  ggplot(aes(uav_tch, lid))+
  geom_point(alpha = 0.8, size = 0.5) +
  #geom_point(aes(uav_cor2, lid)) +
  geom_abline(intercept = 0,slope = 1) +
  xlim(-1, 30) +
  ylim(-1, 30) +
  facet_wrap(~correction, ncol = 3) +
  theme_minimal()

tch %>% 
  # Plot the correction against the LiDAR
  ggplot(aes(uav_cor2, lid, color = as.factor(training)))+
  geom_point(alpha = 0.8) +
  #geom_point(aes(uav_cor2, lid)) +
  geom_abline(intercept = 0,slope = 1) +
  xlim(-1, 30) +
  ylim(-1, 30) 


```







Calculate biomass
```{r biomass, results = "hide"}
lid_agb<-raster_agb2(lid_tch)
uav_agb<-raster_agb2(uav_tch)
uav_cor1_agb<-raster_agb2(uav_tch_cor1)
uav_cor2_agb<-raster_agb2(uav_tch_cor2)
uav_cor3_agb<-raster_agb2(uav_tch_cor3)
uav_cor4_agb<-raster_agb2(uav_tch_cor4)
uav_cor5_agb<-raster_agb2(uav_tch_cor5)
uav_cor6_agb<-raster_agb2(uav_tch_cor6)
uav_cor7_agb<-raster_agb2(uav_tch_cor7)
uav_cor8_agb<-raster_agb2(uav_tch_cor8)

```


The biomass as calculated by the LiDAR and the corrected UAV CHM, shown alongside the 
absolute and relative error, plotted spatially.


```{r plot error against agb}
agb<-data.frame(lid = values(lid_agb), 
           uav = values(uav_agb), 
           uav_cor0 = values(uav_cor1_agb),
           uav_cor1 = values(uav_cor2_agb),
           uav_cor2 = values(uav_cor3_agb),
           uav_cor3 = values(uav_cor4_agb),
           uav_cor4 = values(uav_cor5_agb),
           uav_cor5 = values(uav_cor6_agb),
           uav_cor6 = values(uav_cor7_agb),
           uav_cor7 = values(uav_cor8_agb)) %>%
  na.omit

# Show the overall relationship for the ABG
agb %>% 
  tidyr::gather(key = "uav_chm", value = "uav_agb", uav, matches("uav_cor")) %>%
ggplot(aes(lid, uav_agb)) +
  geom_point(alpha = 0.8, size = 0.5) +
  geom_abline(intercept =0, slope = 1) +
  geom_smooth(method= "lm", formula = y~poly(x, 2)) +
  facet_wrap(~uav_chm)

```

```{r}
# Load in the out of set chm from Bato

lid_bato_chm<-raster("../../data/raster/lid_chm_bato_cropped.tif")
uav_bato_chm<-raster("../../data/raster/uav_chm_bato_georef_cropped.tif")
uav_bato_dsm<-raster("../../data/raster/uav_dsm_bato_georef_cropped.tif")
uav_bato_orig_chm<-raster("../../data/raster/uav_chm_bato_cropped.tif")
uav_bato_orig_dsm<-raster("../../data/raster/uav_dsm_bato_cropped.tif")



# Check the models against each other:
col.pal<-list(color = colorRampPalette(brewer.pal(9,"GnBu"))(10))$color
col.breaks<-seq(0, 50, length=length(col.pal)+1)
par(mfrow=c(1,2))
plot(uav_bato_orig_chm, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
plot(uav_bato_chm, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)


plot(uav_bato_chm - lid_bato_chm)

# The area of the bato survey in hectares:
(sum(is.na(values(lid_bato_chm))) * res(lid_bato_chm)[1] * res(lid_bato_chm)[2]) / 10000

#
#
# Aggregate to TCH ----
#
#

lid_bato_chm[lid_bato_chm<0]<-0
uav_bato_chm[uav_bato_chm<0]<-0
uav_bato_dsm[uav_bato_dsm<0]<-0
uav_bato_orig_chm[uav_bato_orig_chm<0]<-0
uav_bato_orig_dsm[uav_bato_orig_dsm<0]<-0

scale <-50
n_pix<-scale / res(lid_bato_chm)[1]

lid_bato_tch <- aggregate(lid_bato_chm, fact = n_pix, fun = mean_cover)
uav_bato_tch <- aggregate(uav_bato_chm, fact = n_pix, fun = mean_cover)
uav_bato_orig_tch <- aggregate(uav_bato_orig_chm, fact = n_pix, fun = mean_cover)

uav_bato_tch_sd <- aggregate(uav_bato_chm, fact = n_pix, fun = sd)
uav_bato_dsm_1ha<- aggregate(uav_bato_dsm, fact = n_pix, fun = mean_cover)
uav_bato_orig_dsm_1ha<- aggregate(uav_bato_orig_dsm, fact = n_pix, fun = mean_cover)

uav_bato_dsmtpi_2.25ha<- tpiw(uav_bato_dsm_1ha, w = 3, coverage = 0.75)
uav_bato_orig_dsmtpi_2.25ha<- tpiw(uav_bato_orig_dsm_1ha, w = 3, coverage = 0.75)
uav_bato_orig_tch_sd <- aggregate(uav_bato_orig_chm, fact = n_pix, fun = sd)

# Create a raster stack for prediction:
uav_bato_newdata<-stack(uav_bato_tch, uav_bato_dsmtpi_2.25ha, uav_bato_tch_sd)
names(uav_bato_newdata)<-c("uav", "tpi", "tch_sd")

# Predict the corrected values:
uav_bato_tch_cor1 <- raster::predict(uav_bato_newdata, tch_fm1)
uav_bato_tch_cor2 <- sqrt(raster::predict(uav_bato_newdata, tch_fm2))
uav_bato_tch_cor3 <- raster::predict(uav_bato_newdata, tch_fm3)
uav_bato_tch_cor4 <- sqrt(raster::predict(uav_bato_newdata, tch_fm4))
uav_bato_tch_cor5 <- sqrt(raster::predict(uav_bato_newdata, tch_fm5))
uav_bato_tch_cor6 <- sqrt(raster::predict(uav_bato_newdata, tch_fm6))
uav_bato_tch_cor7 <- raster::predict(uav_bato_newdata, tch_fm7)
uav_bato_tch_cor8 <- raster::predict(uav_bato_newdata, tch_fm8)

# And now for the originals...
uav_bato_orig_newdata<-stack(uav_bato_orig_tch, uav_bato_orig_dsmtpi_2.25ha, uav_bato_orig_tch_sd)
names(uav_bato_orig_newdata)<-c("uav", "tpi", "tch_sd")

uav_bato_orig_tch_cor1 <- raster::predict(uav_bato_orig_newdata, tch_fm1)
uav_bato_orig_tch_cor2 <- sqrt(raster::predict(uav_bato_orig_newdata, tch_fm2))
uav_bato_orig_tch_cor3 <- raster::predict(uav_bato_orig_newdata, tch_fm3)
uav_bato_orig_tch_cor4 <- sqrt(raster::predict(uav_bato_orig_newdata, tch_fm4))
uav_bato_orig_tch_cor5 <- sqrt(raster::predict(uav_bato_orig_newdata, tch_fm5))
uav_bato_orig_tch_cor6 <- sqrt(raster::predict(uav_bato_orig_newdata, tch_fm6))
uav_bato_orig_tch_cor7 <- raster::predict(uav_bato_orig_newdata, tch_fm7)
uav_bato_orig_tch_cor8 <- raster::predict(uav_bato_orig_newdata, tch_fm8)


# calculate agb
lid_bato_agb<-raster_agb2(lid_bato_tch)
uav_bato_agb<-raster_agb2(uav_bato_tch)
uav_bato_cor1_agb<-raster_agb2(uav_bato_tch_cor1)
uav_bato_cor2_agb<-raster_agb2(uav_bato_tch_cor2)
uav_bato_cor3_agb<-raster_agb2(uav_bato_tch_cor3)
uav_bato_cor4_agb<-raster_agb2(uav_bato_tch_cor4)
uav_bato_cor5_agb<-raster_agb2(uav_bato_tch_cor5)
uav_bato_cor6_agb<-raster_agb2(uav_bato_tch_cor6)
uav_bato_cor7_agb<-raster_agb2(uav_bato_tch_cor7)
uav_bato_cor8_agb<-raster_agb2(uav_bato_tch_cor8)
uav_bato_orig_agb<-raster_agb2(uav_bato_orig_tch)
uav_bato_orig_cor1_agb<-raster_agb2(uav_bato_orig_tch_cor1)
uav_bato_orig_cor2_agb<-raster_agb2(uav_bato_orig_tch_cor2)
uav_bato_orig_cor3_agb<-raster_agb2(uav_bato_orig_tch_cor3)
uav_bato_orig_cor4_agb<-raster_agb2(uav_bato_orig_tch_cor4)
uav_bato_orig_cor5_agb<-raster_agb2(uav_bato_orig_tch_cor5)
uav_bato_orig_cor6_agb<-raster_agb2(uav_bato_orig_tch_cor6)
uav_bato_orig_cor7_agb<-raster_agb2(uav_bato_orig_tch_cor7)
uav_bato_orig_cor8_agb<-raster_agb2(uav_bato_orig_tch_cor8)

```

```{r TCH independent validation}

tch_bato<-data.frame(lid = values(lid_bato_tch),
                uav = values(uav_bato_tch),
                uav_cor1 = values(uav_bato_tch_cor1),
                uav_cor2 = values(uav_bato_tch_cor2),
                uav_cor3 = values(uav_bato_tch_cor3),
                uav_cor4 = values(uav_bato_tch_cor4),
                uav_cor5 = values(uav_bato_tch_cor5),
                uav_cor6 = values(uav_bato_tch_cor6),
                uav_cor7 = values(uav_bato_tch_cor7),
                uav_cor8 = values(uav_bato_tch_cor8),
                uav_orig = values(uav_bato_orig_tch),
                uav_orig_cor1 = values(uav_bato_orig_tch_cor1),
                uav_orig_cor2 = values(uav_bato_orig_tch_cor2),
                uav_orig_cor3 = values(uav_bato_orig_tch_cor3),
                uav_orig_cor4 = values(uav_bato_orig_tch_cor4),
                uav_orig_cor5 = values(uav_bato_orig_tch_cor5),
                uav_orig_cor6 = values(uav_bato_orig_tch_cor6),
                uav_orig_cor7 = values(uav_bato_orig_tch_cor7),
                uav_orig_cor8 = values(uav_bato_orig_tch_cor8)
                ) %>%
  na.omit

limits<-c(7, 30)


tch_comp_kapas <- tch %>%
  tidyr::gather(key = "correction", value = "uav_tch", uav, matches("uav_cor")) %>%
  mutate(correction = gsub("uav_cor", "Model ", correction)) %>%
  mutate(correction = gsub("uav", "SFM", correction)) %>%
  mutate(correction = relevel(as.factor(correction), ref = "SFM"))
  
tch_comp_bato <- tch_bato %>%
  tidyr::gather(key = "correction", value = "uav_tch",
  uav, matches("uav_cor")) %>%
  mutate(lid2 = lid ^ 2) %>%
  mutate(correction = gsub("uav_cor", "Model ", correction)) %>%
  mutate(correction = gsub("uav", "SFM", correction)) %>%
  mutate(correction = relevel(as.factor(correction), ref = "SFM"))

# Produces the figure showing the TCH comparisons 
pdf("Figures/PeerJ/TCH_correction.pdf",
    width = 5, 
    height = 5)
tch_comp_kapas %>%
  ggplot(aes(uav_tch, lid)) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_point(data = tch_comp_bato, size = 0.5, alpha = 0.5, color = "red") +
  geom_abline(intercept =0, slope = 1) +
  facet_wrap(~correction, ncol = 3) +
  theme_minimal() +
  xlab("SFM (m)") +
  ylab("LiDAR (m)")
dev.off()

tch_comp_kapas %>%
  ggplot(aes(uav_tch, lid2), weight = agb) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_point(data = tch_comp_bato, size = 0.5, alpha = 0.5, color = "red") +
  geom_smooth(method = "lm", formula = y~x) + 
  geom_smooth(method = "lm", formula = y~poly(x, 2, raw = TRUE)) +
  geom_abline(intercept =0, slope = 1) +
  facet_wrap(~correction, ncol = 3) +
  theme_minimal()


tch_bato %>%
  mutate(lidar = lid) %>%
  tidyr::gather(key = "correction", value = "tch", lidar, uav, matches("uav_cor|uav_orig_cor")) %>%
  group_by(correction) %>%
  summarise(tch_mean = mean(tch), 
            tch_sd = sd(tch),
            tch_rsq = summary(lm(lid~tch))$adj.r.squared,
            tch_rmse = rmse(lid, tch),
            tch_bias = bias(lid, tch)
            )


```


```{r}

agb_bato<-data.frame(lid = values(lid_bato_agb),
                uav = values(uav_bato_agb),
                uav_cor1 = values(uav_bato_cor1_agb),
                uav_cor2 = values(uav_bato_cor2_agb),
                uav_orig = values(uav_bato_orig_agb),
                uav_orig_cor1 = values(uav_bato_orig_cor1_agb),
                uav_orig_cor2 = values(uav_bato_orig_cor2_agb)
                ) %>%
  na.omit

tch_bato %>%
  mutate(lid_agb = est_AGB(lid)) %>%
  mutate(lidar = lid) %>%
  tidyr::gather(key = "correction", value = "tch", lidar, uav, matches("uav_cor|uav_orig_cor")) %>%
  mutate(agb = est_AGB(tch)) %>%
  group_by(correction) %>%
  summarise(tch_mean = mean(tch), 
            tch_sd = sd(tch),
            tch_rsq = summary(lm(lid~tch))$adj.r.squared,
            tch_rmse = rmse(lid, tch),
            tch_bias = bias(lid, tch),
            tch_bias75 = bias(lid[lid >= quantile(lid)[4]], tch[lid >= quantile(lid)[4]]),
            agb_mean = mean(agb), 
            agb_sd = sd(agb),
            agb_rsq = summary(lm(lid_agb~agb))$adj.r.squared,
            agb_rmse = rmse(lid_agb, agb),
            agb_bias = bias(lid_agb, agb),
            agb_bias75 = bias(lid_agb[lid >= quantile(lid)[4]], agb[lid >= quantile(lid)[4]]),
            agb_total = sum(agb)
            )
    
# Prepare the data for plotting
agb_comp_kapas <- tch %>%
  mutate(lid_agb = est_AGB(lid)) %>%
  mutate(lidar = lid) %>%
  tidyr::gather(key = "correction", value = "uav_tch",
  uav, matches("uav_cor")) %>%
  mutate(lid2 = lid ^ 2) %>%
  mutate(agb = est_AGB(uav_tch)) %>%
  mutate(correction = gsub("uav_cor", "Model ", correction)) %>%
  mutate(correction = gsub("uav", "SFM", correction)) %>%
  mutate(correction = relevel(as.factor(correction), ref = "SFM"))

agb_comp_bato <- tch_bato %>%
  mutate(lid_agb = est_AGB(lid)) %>%
  mutate(lidar = lid) %>%
  tidyr::gather(key = "correction", value = "uav_tch",
  uav, matches("uav_cor")) %>%
  mutate(lid2 = lid ^ 2) %>%
  mutate(agb = est_AGB(uav_tch)) %>%
  mutate(correction = gsub("uav_cor", "Model ", correction)) %>%
  mutate(correction = gsub("uav", "SFM", correction)) %>%
  mutate(correction = relevel(as.factor(correction), ref = "SFM"))

# Produces the figure showing the AGB comparisons 
pdf("Figures/PeerJ/AGB_correction.pdf",
    width = 5, 
    height = 5)
agb_comp_kapas %>%
  ggplot(aes(agb, lid_agb)) +
  geom_point(size = 0.5, alpha = 0.5) +
  geom_point(data = agb_comp_bato, size = 0.5, alpha = 0.5, color = "red") +
  geom_abline(intercept =0, slope = 1) +
  facet_wrap(~correction, ncol = 3) +
  theme_minimal() +
  xlab(expression(paste("SFM (tonnes ", ha^-1, ")"))) +
  ylab(expression(paste("LiDAR (tonnes ", ha^-1, ")")))
dev.off()

X = rnorm(100, mean =10) # X is a sample of 100 normally distributed random variables
P = ecdf(X)    # P is a function giving the empirical CDF of X
P(0.0)         # This returns the empirical CDF at zero (should be close to 0.5)
plot(P)




mean(agb_bato$lid)
mean(agb_bato$uav)
mean(agb_bato$uav_orig)
mean(agb_bato$uav_cor1)
mean(agb_bato$uav_orig_cor1)
mean(agb_bato$uav_cor2)
mean(agb_bato$uav_orig_cor2)
sd(agb_bato$lid)
sd(agb_bato$uav)
sd(agb_bato$uav_orig)
sd(agb_bato$uav_cor1)
sd(agb_bato$uav_orig_cor1)
sd(agb_bato$uav_cor2)
sd(agb_bato$uav_orig_cor2)
RMSE(obs = agb_bato$lid , pred = agb_bato$uav)
RMSE(obs = agb_bato$lid , pred = agb_bato$uav_orig)
RMSE(obs = agb_bato$lid , pred = agb_bato$uav_cor1)
RMSE(obs = agb_bato$lid , pred = agb_bato$uav_orig_cor1)
RMSE(obs = agb_bato$lid , pred = agb_bato$uav_cor2)
RMSE(obs = agb_bato$lid , pred = agb_bato$uav_orig_cor2)
cor(agb_bato$lid ,agb_bato$uav)
cor(agb_bato$lid ,agb_bato$uav_cor1)
cor(agb_bato$lid ,agb_bato$uav_cor2)
bias(agb_bato$lid ,agb_bato$uav)
bias(agb_bato$lid ,agb_bato$uav_orig)
bias(agb_bato$lid ,agb_bato$uav_cor1)
bias(agb_bato$lid ,agb_bato$uav_orig_cor1)
bias(agb_bato$lid ,agb_bato$uav_cor2)
bias(agb_bato$lid ,agb_bato$uav_orig_cor2)
sum(agb_bato$lid)
sum(agb_bato$uav)
sum(agb_bato$uav_orig)
sum(agb_bato$uav_cor1)
sum(agb_bato$uav_orig_cor1)
sum(agb_bato$uav_cor2)
sum(agb_bato$uav_orig_cor2)



```




```{r Plot AGB and error rasters, echo = FALSE}
par(mfrow=c(1,3), mar = c(0.5,0.5,1,1))
col.pal<-list(color = colorRampPalette(brewer.pal(9,"GnBu"))(10))$color
col.breaks<-seq(0, 120, length=length(col.pal)+1)
# LiDAR measured AGB
plot(lid_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
# UAV measured AGB
plot(uav_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
# Corrected UAV measured AGB
plot(uav_cor2_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)

col.pal<-list(color = colorRampPalette(brewer.pal(9,"RdBu"))(10))$color
col.breaks<-seq(-40, 40, length=length(col.pal)+1)
# Absoute difference
plot((uav_cor8_agb - lid_agb), col = col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
col.pal<-list(color = colorRampPalette(brewer.pal(9,"RdBu"))(10))$color
col.breaks<-seq(-1.5, 1.5, length=length(col.pal)+1)
# Relative difference
plot((uav_cor8_agb - lid_agb)/lid_agb, col = col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
```


```{r Plot Bato AGB and error rasters, echo = FALSE}
par(mfrow=c(2,2), mar = c(0.5,0.5,1,1))
col.pal<-list(color = colorRampPalette(brewer.pal(9,"GnBu"))(10))$color
col.breaks<-seq(0, 150, length=length(col.pal)+1)
# LiDAR measured AGB
plot(lid_bato_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
# UAV measured AGB
plot(uav_bato_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
# Corrected UAV measured AGB
plot(uav_bato_cor1_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
# Corrected UAV measured AGB
plot(uav_bato_orig_cor1_agb, col=col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)

#writeRaster(uav_bato_cor2_agb - lid_bato_agb, "../../data/raster/agb_bato_liduav_diff.tif")

col.pal<-list(color = colorRampPalette(brewer.pal(9,"RdBu"))(10))$color
col.breaks<-seq(-40, 40, length=length(col.pal)+1)
# Absoute difference
plot((uav_bato_cor1_agb - lid_bato_agb), col = col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
col.pal<-list(color = colorRampPalette(brewer.pal(9,"RdBu"))(10))$color
col.breaks<-seq(-0.5, 0.5, length=length(col.pal)+1)
# Relative difference
plot((uav_bato_cor1_agb - lid_bato_agb)/lid_bato_agb, col = col.pal, breaks=col.breaks, colNA='black', axes=FALSE, legend=TRUE, box=FALSE)
```


```{r}
sum(agb_bato$lid, na.rm = TRUE)
sum(agb_bato$uav, na.rm = TRUE)
sum(agb_bato$uav_cor1, na.rm = TRUE)
sum(agb_bato$uav_cor2, na.rm = TRUE)
sum(agb_bato$uav_orig_cor2, na.rm = TRUE)
```

```{r}
#
#
# Compare distributions ----
#
# Compare the distribution of top canopy height when calculated from the
# original CHM and the georeferenced CHM.
#
#

# Mask lidar and uav to each others' extent
uav_dsm_orig<-raster("data/raster/uav_dsm_bato_cropped.tif")
uav_chm_orig<-raster("data/raster/uav_chm_bato_cropped.tif")

uav_chm_orig<-uav_dsm-uav_dtm
uav_chm_orig[uav_chm_orig<0]<-NA
uav_chm_orig[uav_chm_orig>70]<-NA

uav_chm_georef<-raster("../../data/raster/Products/CHM_photoscan_wo_markers7and8_georef.tif")
range(values(uav_chm_georef), na.rm = TRUE)
uav_chm_georef[uav_chm_georef<0]<-NA
uav_chm_georef[uav_chm_georef>70]<-NA

# Crop the lidar rasters to the extent of the UAV DSM
uav_chm_orig<-crop(uav_chm_orig, min_extent(uav_chm_orig, uav_chm_georef))
uav_chm_georef<-crop(uav_chm_georef, min_extent(uav_chm_orig, uav_chm_georef))

par(mfrow=c(1,2))
plot(uav_chm_orig)
plot(uav_chm_georef)

uav_chm_georef<-resample(uav_chm_georef, uav_chm_orig) # Align the rasters

uav_chm_georef<-mask(uav_chm_georef, uav_chm_orig) # crops uav to lidar
uav_chm_orig<-mask(uav_chm_orig, uav_chm_georef) # crops lidar to new uav extent
uav_chm_georef<-mask(uav_chm_georef, uav_chm_orig) # crops uav to new lidar extent - they should be the same now

# trim off the NAs
uav_chm_orig <- trim(uav_chm_orig)
uav_chm_georef <- trim(uav_chm_georef)

par(mfrow=c(1,2))
plot(uav_chm_orig)
plot(uav_chm_georef)

# Now crop away the distorted margin:
aoi<-drawPoly(sp=TRUE, col='red', lwd=2) # !!! You have to do this by hand on the plotted image
plot(aoi, col = "blue", add = TRUE)
uav_chm_orig<-mask(uav_chm_orig, aoi)
uav_chm_georef<-mask(uav_chm_georef, aoi)
uav_chm_orig <- trim(uav_chm_orig)
uav_chm_georef <- trim(uav_chm_georef)

```

```{r}
# Convert to TCH
scale <-100
n_pix<-as.integer(scale / res(uav_chm_orig)[1])
uav_tch_orig <- aggregate(uav_chm_orig, fact = n_pix, fun = mean)
uav_tch_georef <- aggregate(uav_chm_georef, fact = n_pix, fun = mean)


tch<-rbind(data.frame(model = "orig", tch = values(uav_tch_orig)),
           data.frame(model = "georef", tch = values(uav_tch_georef))
)

# Plot out
tch %>%
  ggplot(aes(tch)) +
  geom_histogram(alpha = 0.5) +
  facet_wrap(~model, nrow = 2)

# They are very similar
```


